MG7: Configurable and scalable 16S data analysis

### 2016-07-25 docs/mg7-paper/out/paper.tex
no 16S metagenomics, only 16S data analysis
fix keywords

\title{MG7: Configurable and scalable 16S metagenomics data analysis}

@@

\keywords{ Metagenomics, 16S, Bacterial diversity profile, Bio4j, Graph databases,
 Cloud computing, NGS, Genomic big data, Microbiome, Environmental, 16S
 Database}

>>>>

\title{MG7: Configurable and scalable 16S data analysis}

@@

\keywords{ Metagenomics, 16S, taxonomic profiling, Bio4j, Graph databases, Cloud
 computing, NGS, Genomics, big data, Microbiome, Environmental, 16S
 Database}
